---
title: First Post!
author: Eugenio Palmieri
date: '2017-08-29'

slug: primo-post
categories:
  - web
tags:
  - web
  
summary: "An illustration of the main feautures of my new blog, Computation Debate. The blog will be mainly about Statistics, Informatics, Programming, Politics, Economics and Urban Planning."

---


## Hello World,

welcome to *Computation Debate* [^1], my new personal blog. My name is Eugenio Palmieri and I'm a Master's student in Statistics at Florence University (Italy) and I want to write mainly about statistics, informatics and programming[^2], but I'm interested also in economics, politics, urban planning, mathematics and other nerdy topics.

## Feautures of the blog:

I want to describe with some examples the main features of the blog, especially  for other statistics or other R (a programming language) users like me. In my next post I am going to explain how to [build a blog like this for free](https://palmierieugenio.github.io/post/build-a-blog-with-hugo-github-and-blogdown/).

I don't plan to make all my posts about programming or *topics for nerd*, I want to make more accessible contents in the future, but, for now, if you aren't into this kind of things, I warn you that your eyes could bleed.


### Integration with R:
One of the main feature of this blog is that it supports [Rmarkdown](http://rmarkdown.rstudio.com/) files, which make it possible to create post from Rstudio to generate directly graphs, tables and interactive [html widgets](http://www.htmlwidgets.org/) with R[^3], like in this graph example:

```{r graficoesempio}
library(ggplot2)

data=data.frame(cond = rep(c("condition_1", "condition_2"), each=10), my_x = 1:100 + rnorm(100,sd=9), my_y = 1:100 + rnorm(100,sd=16) )

ggplot(data, aes(x=my_x, y=my_y)) + geom_point(shape=1) +  
geom_smooth(method=lm , color="red", se=TRUE)
```

Or in this example of interactive time-series chart:

```{r seriestoriche}
library(dygraphs)
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths)%>% dyRangeSelector()
```

<br>
<br>

## Support for [$\rm \LaTeX$ math expressions](https://en.wikibooks.org/wiki/LaTeX/Mathematics):
Anothere important feauture is the support for $\rm \LaTeX$ to write equations and formulas:
```teX
$$\mathbf{y} = \mathbf{X}\boldsymbol\beta + \boldsymbol\varepsilon$$
```

$$\mathbf{y} = \mathbf{X}\boldsymbol\beta + \boldsymbol\varepsilon$$
<br>

## Other programming languages:

With the `knitr` [package](https://yihui.name/knitr/demo/engines/) is possible to use chunks of code from other language engines (like Python, C, Ruby, SQL, Bash, Rcpp, Stan, JavaScript, Perl, SAS, Scala and CSS) directly [from Rstudio](http://rmarkdown.rstudio.com/authoring_knitr_engines.html) .

### C++
This is an example of C++ code compiled through the `Rcpp`[^4] package, inside a `{r engine='Rcpp'}` code chunk:

```{r engine='Rcpp'}
#include <Rcpp.h>
// [[Rcpp::export]]
double sumRcpp(const Rcpp::NumericVector& x) {
    std::size_t n = x.size();
    double total = 0;
    if (n > 0) {
        for (std::size_t i = 0, k = n - 1; i < k; ++i, --k)
            total += x[i] + x[k];
        if (n % 2 == 1)
            total += x[n / 2];
    }
    return total;
}
```

Compare, in a R chunk of code[^5], the new defined `sumRcpp()` function with the normal R `sum()`:
```{r, warning=FALSE, message=F, cache = TRUE}
library(microbenchmark)
library(ggplot2)
theme_set(theme_bw())
bench <- function(..., n = 10e2 * 1:10e2, times = 100) {
    exprs <- as.list(match.call(expand.dots = FALSE)$...)
    nexprs <- length(exprs)
    nout <- nexprs * times
    out <- list(n = integer(nout),
                expr = factor(integer(nout), levels = as.character(exprs)),
                time = numeric(nout))
    for (i in seq_along(n)) {
        start <- (i - 1) * nexprs + 1
        end <- start + nexprs - 1
        x <- runif(n[i])
        res <- microbenchmark(list = exprs, times = times)
        res <- stack(lapply(split(res$time, res$expr), median.default))
        out[["n"]][start:end] <- n[i]
        out[["expr"]][start:end] <- res$ind
        out[["time"]][start:end] <- res$values
    }
    class(out) <- "data.frame"
    attr(out, "row.names") <- .set_row_names(length(out$n))
    gp <- ggplot(out, aes(x = n, y = time, linetype = expr, color = expr)) +
        geom_smooth(se = FALSE)
    print(gp)
    invisible(out)
}

bench(sum(x), sumRcpp(x))
```

### Python

Using the Python Engine directly from Rstudio, inside a `{python}` code chunk:

```{python}
import sys
print(sys.version)
```

It is even possible to exchange data frames from R and Python via a file system with the `feather` [package](https://blog.rstudio.com/2016/03/29/feather/).

### Modify the structure of the blog with Widgets
The original structure of the site after the installation is like [this](https://sourcethemes.com/academic/). I made some modification, deleting some widgets (part of the site) I wasn't using. If you want to know more about the widgets supported by this template, look here at the [documentation](https://sourcethemes.com/academic/post/widgets/).

## [Build your own blog for free!](https://palmierieugenio.github.io/post/build-a-blog-with-hugo-github-and-blogdown/)
If you are interested in building a blog like this for free, you can read the new post I've made to explain how to [create a blog with Hugo and Github](https://palmierieugenio.github.io/post/build-a-blog-with-hugo-github-and-blogdown/) with the [blogdown package](https://github.com/rstudio/blogdown), directly from Rstudio.

<br>

[^1]: The title is inspired by the [Socialist calculation debate](https://en.wikipedia.org/wiki/Socialist_calculation_debate) and by Kantorovich and his works, like *Mathematical Methods of Organizing and Planning Production*.

[^2]: I'm using mainly R with RStudio, but I have some basic experience with Stata, Systat, GeoDa, Qgis, Markdown, Rmarkdown, LaTex and I'm intentioned to learn Python.

[^3]: [R](https://www.r-project.org/) is a a free software environment for statistical computing and graphics and [Rstudio](https://www.rstudio.com) is an integrated development environment (IDE) for R.

[^4]: The `Rcpp` is slightly different from the other languages that can use the engine directly, with something like `{python, engine.path="/Users/me/anaconda/bin/python"}`.

[^5]: I suggest you to use the option `cache = TRUE` in the chunk of codes that need a relatively long time to run, so it will save the output and the code won't run every time you use the `blogdown:::serve_site()` command.