---
title: provaEU
author: Eugenio Palmieri
date: '2017-08-22'
slug: provaeu
categories:
  - test
tags:
  - test
---

PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVAPROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA
PROVA PROVA

Pacchetti:
```{r, echo=T,message=FALSE,warning=FALSE, tidy=TRUE}
library(ggplot2)
library(plotly)
library(CatterPlots)
```

Grafici:
```{r, warning=FALSE, tidy=TRUE}

p <- ggplot(data = diamonds, aes(x = cut, fill = clarity)) +
            geom_bar(position = "dodge")
ggplotly(p)
```

```{r, warning=FALSE}
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width)) + 
    geom_point()
 
```

```{r}
x <- -10:10
y <- -x^2 + 10
meow <- multicat(xs=x, ys=rnorm(21),
                 cat=c(1,2,3,4,5,6,7,8,9,10),
                 catcolor=list(c(0,0,0,1)),
                 canvas=c(-0.1,1.1, -0.1, 1.1),
                 xlab="some cats", ylab="other cats", main="Random Cats")
```

