---
title: First Post!
author: Eugenio Palmieri
date: '2017-08-27'

slug: primo-post
categories:
  - comunicazioni
tags:
  - comunicazioni
---

## Hello World, welcome to NOME BLOG,

My name is Eugenio Palmieri and I'm starting a new personal blog. I'm a Master's student in Statistics at Florence University (Italy) and I want to write mainly about statistics, informatics and programming[^1], but I'm interested also in economics, politics, urban planning, mathematics and other nerdy topics.

## Feautures of the blog:

### Integration with R:
One of the main feauture of this blog is that it supports [Rmarkdown](http://rmarkdown.rstudio.com/) files, which make it possible to create post from Rstudio to generate directly graphs, tables and interactive [html widgets](http://www.htmlwidgets.org/) with R[^2], like in this graph example:

```{r graficoesempio}
library(ggplot2)

data=data.frame(cond = rep(c("condition_1", "condition_2"), each=10), my_x = 1:100 + rnorm(100,sd=9), my_y = 1:100 + rnorm(100,sd=16) )

ggplot(data, aes(x=my_x, y=my_y)) + geom_point(shape=1) +  
geom_smooth(method=lm , color="red", se=TRUE)
```

Or in this example of interactive time-series chart:

```{r seriestoriche}
library(dygraphs)
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths)%>% dyRangeSelector()
```

<br>

## Support for [$\rm \LaTeX$ math expressions](https://en.wikibooks.org/wiki/LaTeX/Mathematics):
Anothere important feauture is the support for $\rm \LaTeX$ to write equations and formulas:
```teX
$$\mathbf{y} = \mathbf{X}\boldsymbol\beta + \boldsymbol\varepsilon$$
```

$$\mathbf{y} = \mathbf{X}\boldsymbol\beta + \boldsymbol\varepsilon$$
<br>

## Build your own blog for free!
If you are interested in building a blog like this for free, you can read the new post I've made to explain how to [create a blog with Hugo and Github](#rotto) with the [blogdown package](https://github.com/rstudio/blogdown), directly from Rstudio.

<br>

[^1]: I'm using mainly R with RStudio, but I have some basic experience with Stata, Systat, GeoDa, Qgis, Markdown, Rmarkdown, LaTex and I'm intentioned to learn Python.

[^2]: [R](https://www.r-project.org/) is a a free software environment for statistical computing and graphics and [Rstudio](https://www.rstudio.com) is an integrated development environment (IDE) for R.